Dark energy is based on a math error from 1930

### 2024-12-28 paper/paper.tex

\begin{figure}[h]
  \includegraphics[width=\linewidth]{K-corrections_for_photon_counts.png}
  \caption{An example of how K-corrections take an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the bandwidth spectrum warping effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band B filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of K-corrections is based on the work of \citet{kim1996}.
This work extended the calculations of K-corrections to extend to filters
beyond B and V. It also introduced a term that deals with the zero-point for the
actual filters. Equation 2 from this paper is the form of the K-corrections
used in the modern day:

\begin{equation}
\label{eq:kim2}
  K_{xy} =
    -2.5\text{log} \left(
      \frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
           {\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
    + 2.5\text{log}(1+z)
    + 2.5\text{log}\left(
      \frac{\int F(\lambda)S_x(\lambda)d\lambda}
           {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
\end{equation}

This equation has two problems with it, which we will explore in Section
\ref{sec:derivation}.

@@

The definition of K-corrections is

\begin{equation}
\begin{aligned}
\label{eq:definition}
  m_x &= M_x + \mu + K_{xy} \\
      &= M_x + m_y - M_y + K_{xy} \\
      &= m_y + K_{xy}.
\end{aligned}
\end{equation}

The second line of Equation \ref{eq:definition} expands the distance modulus
$\mu$ using $\mu = m = M$ where $m$ is the observed magnitude and $M$ is the
absolute magnitude. Since the absolute magnitude is an intrinsic property of a
stellar object, we can use $M = M_x = M_y$, so the absolute magnitude terms
cancel out in the third line.

We will also need to use the flux to magnitude formula:

\begin{equation}
\begin{aligned}
\label{eq:flux2mag}
  m_x &= -2.5 \text{log}(\mathcal{F}_x) + C_x \\
      &= -2.5 \text{log}(C'_x \mathcal{F}_x) .
\end{aligned}
\end{equation}

Here, $C_x$ represents the zero-point for the filter $x$ on some particular
telescope. In order to use consistend magnitude values across different
telescopes that have different light gathering powers, we take the measured
magnitude and multiply it by the ratio of the flux rate for the standard
telescope and filter to the flux rate for this particular telescope and
filter.

Since the K-correction is a magnitude value, we can define

\begin{equation}
K_x = -2.5\text{log}(k_x C_x)
\end{equation}

and use Equation \ref{eq:flux2mag} to recombine the flux term $\mathcal{F}_y$
with $m_y$ from Equation \ref{eq:definition}. This gives

\begin{equation}
\begin{aligned}
            m_x &= -2.5 \text{log}(\mathcal{F}_y) + K_{xy} \\
                &= -2.5 \left( \text{log}(\mathcal{F}_y) + \text{log}(k_x C_x) \right) \\
                &= -2.5 \text{log}(\mathcal{F}_y \times k_{xy} \times C_x) \\
  \mathcal{F}_x &= \mathcal{F}_y \times k_{xy} \times C_x .
\end{aligned}
\end{equation}

The work up to this point has been to translate the K-corrections equation from
a magnitude problem to a flux problem. This has intuitive benefits, at least
for the authors. The goal is to make $k_{xy}$ equal the ratio of the flux rate
that we want in filter $x$ to the flux rate that we observe in filter $y$.

The first term of this equation deals with zero-points $C$, which is a
magnitude added to individual filters to correct for the light gathering
abilities of the filter together with the telescope. We are converting the
magnitude from the $y$ filter to the $x$ filter by using $m_x = m_y - k_{xy}$,
so $k_{xy}$ needs to include $C_y - C_x$.

The numerator of the third term, $\int F(\lambda)S_x(\lambda)d\lambda$,
measures what the flux would be if there was no redshift in the target filter.
The denominator $\int F(\lambda/(1+z))S_y(\lambda))d\lambda$ takes the
observation filter's sensitivity $S_y(\lambda)$ at each wavelength $\lambda$
and multiples it by the rest frame spectral energy density $F(\lambda/(1+z))$
that corresponds to the blueshifted wavelength $\lambda / (1+z)$.

The effect of
multiplying the filter sensitivity $S(\lambda)$ by the blueshifted spectral energy density $F(\lambda / (1+z))$ is the same as if we created a new
spectral energy density $F'(\lambda) = F(\lambda / (1+z))$. The key thing to
notice with $F'$ is that it artificially inflates the total amount of flux by a
factor of $1 + z$. That is,

\begin{equation}
(1+z) \times \int_{a}^{b} S(\lambda) d\lambda = \int_{a(1+z)}^{b(1+z)} S'(\lambda) d\lambda .
\end{equation}

In order to discuss flux instead of magnitude, we can rewrite Equation \ref{eq:kim2} as

\begin{equation}
\begin{aligned}
\label{eq:kim_flux}
  K_{xy} &= -2.5 \text{log}(\mathcal{F}) + C_x - C_y \\
         &= -2.5 \text{log}\left(
              \frac{(1+z) \int F(\lambda)S_x(\lambda)d\lambda}
                   {\int F(1/(1+z))S_y(\lambda))d\lambda}\right) + C_x - C_y \\
  \mathcal{R} &= (1+z) \times \frac{\int F(\lambda)S_x(\lambda)d\lambda}
                                   {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}
\end{aligned}
\end{equation}

where $C_x$ and $C_y$ represent the zero-point magnitudes for the target filter
and the observation filter respectively.

at a
blueshifted wavelength given by $F(\lambda / (1+z))$. In other words, it calculates what the observation filter would measure if it was blue shifted.

if the observation filter were blueshifted, similar to the top-right panel of Figure \ref{fig:k-example}, the denominator

the flux that would be measured

The next major advance in K-corrections was

\citet{snpy}

>>>>

\begin{figure}[H]
  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
  \caption{An example of how K-corrections take an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the bandwidth spectrum warping effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band B filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of K-corrections is based on the work of \citet{kim1996}.
This work extended the calculations of K-corrections to extend to filters
beyond B and V. It also introduced a term that deals with the zero-point for
the actual filters. In the modern day, filters measure the photon flux as
upposed to the energy flux. Historically, bolometric devices would measure the
energy flux, but modern CCD cameras effectively measure the photon flux.

Quoting \citet{kim1996}:

\begin{quote}
  Therefore, the correct K correction caluculation to be used with measured
  photometric magnitudes is the integral photon counts:

  \begin{equation}
  \label{eq:kim}
    K_{xy} =
      -2.5\text{log} \left(
        \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
      + 2.5\text{log}(1+z)
      + 2.5\text{log}\left(
        \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
             {\int \lambda F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
  \end{equation}
\end{quote}

This equation has three errors, which we will explore in Section
\ref{sec:consequences}.

@@

With modern CCD cameras, a telescope observaion consists of a single value
$\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
second. A summary of how this works is provided by \citet{lesser2015}. The
measured energy is produced by electrons not photons, so the measured number is
proportional to the number of photons. However, we need to calculate the
expected number of photons collected by using a spectral energy density
function $F$. The value $F(\lambda)$ gives the amount of energy collected by a
bolometric device for the wavelength $\lambda$.

To convert the spectral energy density $F$ to the photon density $F'$, we need
to use the Plank relation $E = \frac{hc}{\lambda}$ where $E$ is the energy, $h$
is Planck's constant, and $c$ is the speed of light. This gives us

\begin{equation}
\begin{aligned}
   F(\lambda) &= F'(\lambda) \times \frac{hc}{\lambda} \\
  F'(\lambda) &= \frac{\lambda F(\lambda)}{hc}.
\end{aligned}
\end{equation}

It's important to note that for the blueshifted wavelength $\lambda / (1+z)$,
this equation produces

\begin{equation}
 F'\left(\frac{\lambda}{1+z}\right) = \frac{\left(\frac{\lambda}{1 + z}\right) F\left(\frac{\lambda}{1+z}\right)}{hc}.
\end{equation}

However, this equation is misleading and error prone. We will want to use it to
help calculate the amount of flux in an observation filter at the redshifted
wavelength $\lambda \times (1 + z)$. In other words, we want to produce the
photon density function $R'$ that is the redshifted version of $F'$.
Redshifting does two things:

\begin{itemize}
  \item The stretching of space increases the distance between photons while
  they are traveling. This phenomenon appears to an observer like time
  dilation, although cosmological time dilation is due to a different mechanism
  than relativistic time dilation. This effect reduces the photon arrival rate
  by a factor of $1/(1+z)$.

  In order to account for cosmological time dilation, we will need to multiply
  $F'$ by $1/(1+z)$.

  \item All wavelengths are changed by a factor of $1 + z$. When we integrate
  $R'$ from wavelength $\lambda_a$ to wavelength $\lambda_b$, the values
  correspond to the wavelengths $\lambda_a / (1+z)$ to $\lambda_b / (1+z)$ in
  $F'$. We will integrate over a width of $\lambda_b - \lambda_a$, but
  $F'(\lambda / (1+z))$ will refer to values in a width of
  $(\lambda_b - \lambda_a) / (1+z)$.

  In order to account for this bandwidth spectral warping effect, we will need
  to multiply $F'$ by a second factor of $1/(1+z)$.
\end{itemize}

Combining these two phenomena together, we can calculated the redshifted
spectral energy density $R$ using

\begin{equation}
\begin{aligned}
\label{eq:redshifted_density}
  R'(\lambda) &= F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} \\
  R(\lambda) &= \frac{F(\lambda / (1+z))}{(1+z)hc} \times \frac{1}{(1 + z)^2} .
\end{aligned}
\end{equation}

In order to calculate the amount of flux $\mathcal{F}_x$ measured in filter
$x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
sensity $S_x(\lambda)$, which represents the proportion of photons filter $x$
will measure at wavelength $\lambda$. We then need to sum over all wavelengths,
which is expressed with the equation

\begin{equation}
\begin{aligned}
\label{eq:flux_definition}
  \mathcal{F}_x &= \int F'(\lambda) S_x(\lambda) d\lambda \\
                &= \int \lambda F(\lambda) S_x(\lambda) d\lambda.
\end{aligned}
\end{equation}

The limits of integration are techinically from 0 to $\infty$, but these are
usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
outside of a filter's bandpass.

We will also use the energy flux $\mathcal{F}$ to magnitude $m$ formula:

\begin{equation}
\begin{aligned}
\label{eq:flux2mag}
                             m_x &= -2.5 \text{log}(\mathcal{F}_x) + P_x \\
  -2.5 \text{log}(\mathcal{F}_x) &= m_x - P_x .
\end{aligned}
\end{equation}

$P_x$ represents the zero-point for the filter $x$ on some particular
telescope. In order to use consistant magnitude values across telescopes that
have different light gathering abilities, we take the measured magnitude and
multiply it by the ratio of the standard flux rate to the flux rate for this
particular telescope and filter. For convenience, we use $P_x = -2.5
\text{log}(P'_x)$ so that we can work with flux instead of with magnitude.

Now that we have the identities in Equations \ref{eq:flux_definition} and
\ref{eq:flux2mag} we will change directions and look at the definition of
K-corrections $K_{xy}$. This value allows us to make an observation in filter
$y$ and report what the magnitude would have been in filter $x$ if no redshift
occured:

\begin{equation}
\begin{aligned}
\label{eq:definition}
  m_y &= M_x + \mu + K_{xy} \\
      &= M_x + m_x - M_x + K_{xy} \\
      &= m_x + K_{xy} \\
  m_x &= m_y - K_{xy} .
\end{aligned}
\end{equation}

The second line of Equation \ref{eq:definition} expands the distance modulus
$\mu$ using $\mu = m - M$ where $m$ is the observed magnitude and $M$ is the
absolute magnitude.

Since the K-correction is a magnitude value and we wish to work on flux values,
it is convenient to define the following substitution:

\begin{equation}
\label{eq:k_substitution}
  K_{xy} = 2.5\text{log}(K'_{xy}) .
\end{equation}

Note that this substitution omits the minus ($-$) sign.

Starting with Equation \ref{eq:flux2mag} and then
recombining the flux term $\mathcal{F}_y$ with $m_y$ from Equation
\ref{eq:definition}, we have

\begin{equation}
\begin{aligned}
\label{eq:as_flux}
  -2.5 \text{log}(\mathcal{F}_x)
      &= m_x - P_x \\
      &= m_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y)
         - 2.5 \text{log}(P'_y)
         - 2.5 \text{log}(K'_{xy})
         + 2.5 \text{log}(P_x) \\
      &= -2.5 \left(
         \text{log}(\mathcal{F}_y)
         + \text{log}(K'_{xy})
         + \text{log}(P'_y)
         - \text{log}(P'_x)
        \right) \\
      &= -2.5 \text{log}\left(
        \mathcal{F}_y
        \times K'_{xy}
        \times \frac{P'_y}{P'_x}\right) \\
  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x}.
\end{aligned}
\end{equation}

It's useful to inspect this equation to consider whether the term
$\frac{P'_y}{P'_x}$ is correct, or if it might be flipped to the inverse of
what it should be. However, if we rewrite Equation \ref{eq:as_flux} as

\begin{equation}
  \mathcal{F}_x \times P'_x = \mathcal{F}_y \times P'_y \times K'_{xy}
\end{equation}

then the meaning is a bit more clear. The left hand side
$\mathcal{F}_x \times P'_x$ is the rate of photon collection for an idealized
telescope in filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon
collection for an idealized telescope in filter $y$. We are able to observe the
value $\mathcal{F}_y \times P'_y$ and want to use the fudge factor $K'_{xy}$ to
produce the value $\mathcal{F}_x \times P'_x$.

We can isolate $K'_{xy}$ and then use Equation \ref{eq:flux_definition} to expand

\begin{equation}
\begin{aligned}
  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x} \\
        K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} .
\end{aligned}
\end{equation}

Now we use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
spectral energy density function $F$. Note that $\mathcal{F}_x$ uses the rest
frame spectral energy density $F$ while $\mathcal{F}_y$ uses the redshifted
spectral energy density $R(\lambda)$:

\begin{equation}
\begin{aligned}
  K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} \\
         &= \frac{P'_x \int F'(\lambda) S_x d\lambda}
                 {P'_y \int R'(\lambda) S_y d\lambda} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x d\lambda}
                   {\int F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
              \frac{\int \frac{\lambda F(\lambda)}{hc} S_x d\lambda}
                   {\int \frac{F(\lambda / (1+z))}{(1+z)hc} S_y d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} .
\end{aligned}
\end{equation}

Finally, we can use Equation \ref{eq:k_substitution} to convert the flux $K'_{xy}$ back
into the magnitude $K_{xy}$:

\begin{equation}
\begin{aligned}
\label{eq:K2k}
  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
         &= 2.5\text{log}\left(
            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
            \frac{\int \lambda F(\lambda) S_x d\lambda}
                 {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}\right) \\
         &= 2.5 \left(
            \text{log} \left( \frac{P'_x}{P'_y} \right)
            + \text{log}( {(1 + z)^2})
            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}
            \right) \right) \\
         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
            - P_x + P_y .
\end{aligned}
\end{equation}

\section{Consequences}
\label{sec:consequences}

In order to fully compare our derivation against Equation \ref{eq:kim}, we need
to use the identity

\begin{equation}
  P = -2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
\end{equation}

where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an idealized
spectral energy distribution at $z = 0$ for which $U = B = V = R = I = 0$ in
the photometric system being used." Combining this with Equation \ref{eq:K2k}, we have

\begin{equation}
\begin{aligned}
  K_{xy} &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
            - P_x + P_y \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
            + 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
            - 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
         &= 2.5 \text{log} \left(
              \frac{\int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
                   {\int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
             \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x d\lambda}
                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) .
\end{aligned}
\end{equation}
